%\documentclass[a4paper,12pt,notitlepage]{report}
\documentclass[a4paper,12pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}
%\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{mathrsfs}

%\usepackage{makeidx}
\usepackage{import}
%\usepackage{theoremref}
%\usepackage{hyperref}
%\usepackage{fancyref}

\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{verbatim}
\usetikzlibrary{%
  matrix,%
  calc%
}

\title{El teorema de Stark-Heegner v\'{\i}a curvas modulares %
	asociadas a subgrupos de Cartan \textit{non-split} %
	de $\GL{2}(\bb{Z}/N\bb{Z})$}
\author{Daniel Mejail}
\date{26/09/2016}

\pdfinfo{%
  /Title    ()
  /Author   ()
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords ()
}

%elements of style
\usepackage{sectsty}
%\usepackage{titlesec}
%
\pagestyle{plain}
\allsectionsfont{\rmfamily \mdseries \scshape \centering}
%changing names
\renewcommand{\refname}{Bibliograf\'{\i}a}
%{\rmfamily \mdseries \scshape \centering Bibliograf\'{\i}a}
%this is not needed since we're using the ``\allsectionsfont''
%command

%commands and theorems
\input{./comms/comms.tex}
\input{./thms/thms.tex}

\begin{document}
\maketitle
\begin{section}{Introducci\'{o}n}\label{sec:intro}
 \input{./files/intro.tex}

 \begin{subsection}{El teorema de Stark-Heegner %
			y su relaci\'{o}n con formas %
			cuadr\'{a}ticas}\label{subsec:losNueve}
 \input{./files/losNueveCuerpos.tex}%introducci\'{o}n, algo de [[serre]]
 \end{subsection}
\end{section}

\begin{section}{Generalidades}%{\mdseries \scshape Generalidades}
 \label{sec:generalidades}
 \input{./files/generalidades.tex}

 \begin{subsection}{Parametrizaciones}\label{subsec:params}
  \input{./files/paramsChen.tex}
 \end{subsection}

 \begin{subsection}{Ramificaci\'{o}n}\label{subsec:ram}
  \input{./files/ramBaran.tex}
 \end{subsection}
\end{section}
 
\begin{section}{Soluciones al problema del n\'{u}mero de %
		clases igual a $1$}\label{sec:soluciones}
 \begin{subsection}{Nivel $24$}\label{subsec:nivelVeinticuatro}
  \input{./files/nivel24.tex}
 \end{subsection}

 \begin{subsection}{Nivel $7$}\label{subsec:nivelSiete}
  \input{./files/nivel7.tex}
 \end{subsection}

 \begin{subsection}{Nivel $5$ (o $15$)}\label{subsec:nivelCinco}
  \input{./files/nivel5.tex}
 \end{subsection}

 \begin{subsection}{Nivel $9$}\label{subsec:nivelNueve}
  \input{./files/nivel9.tex}
 \end{subsection}

 \begin{subsection}{Nivel $11$}\label{subsec:nivelOnce}
  \input{./files/nivel11.tex}
 \end{subsection}
\end{section}

\begin{thebibliography}{99}

 \bibitem{baranLevelNine} B. Baran. \emph{A Modular Curve of Level
 $9$ and the Class Number One Problem}. Journal of Number Theory,
 129 (2009), 715-728.

 \bibitem{baranNormalizers} B. Baran. \emph{Normalizers of
 Non-split Cartan Subgroups, Modular Curves, and the Class Number
 One Problem}. Journal of Number Theory, 130 (2010), 2753-2772.

 \bibitem{baranAnExceptionalIso} B. Baran. \emph{An Exceptional
 Isomorphism Between Modular Curves of Level $13$}. Journal of Number
 Theory, 145 (2014), 273-300.

 \bibitem{booher} J. Booher. \emph{Modular Curves and the Class
 Number One Problem}.

 \bibitem{chenLevelFive} I. Chen. \emph{On Siegel's Modular Curve
 of Level $5$ and the Class Number One Problem}. Journal of
 Number Theory, 74 (1999), 278-297.

 \bibitem{cox} D. A. Cox. \emph{Primes of the Form $x^{2}+ny^{2}$:
 Fermat, Class Field Theory, and Complex Multiplication}. Wiley, 1989.

 \bibitem{deligneRapoport} P. Deligne, M. Rapoport. \emph{Les sch\'{e}mas
 de modules de courbes elliptiques}. Antwerp, 1972.

 \bibitem{diamondShurman} F. Diamond, J. Shurman. \emph{A
 First Course in Modular Forms}. Springer-Verlag New York, 2005.

 \bibitem{kenkuLevelSeven} M. A. Kenku. \emph{A Note on the Integral
 Points of a Modular Curve of Level $7$}. Mathematika, 32 (1985),
 45-48.

 \bibitem{ligozat} G. Ligozat. \emph{Courbes modulaires de niveau $11$}.
 En J.-P. Serre, D. Zagier, eds. \emph{Modular Functions of One Variable},
 vol. V. Springer-Verlag New York, 1977.

 \bibitem{schoofTzanakisLevelEleven} R. Schoof, N. Tzanakis.
 \emph{Integral Points of a Modular Curve of Level $11$}. Acta
 Arithmetica, 152 (2012), 39-49.

 \bibitem{stroekerTzanakis} R. J. Stroeker, N. Tzanakis.
 \emph{Solving Elliptic Diophantine Equations by Estimating Linear Forms
 in Elliptic Logarithms}. Acta Arithmetica, 67 (1994), 177-196.

 \bibitem{serre} J.-P. Serre. \emph{Lectures on the
 Mordell-Weil Theorem}. $3^{a}$ ed. Vieweg+Teubner Verlag, 1997.

\end{thebibliography}
\end{document}
